### 2018-01-25 ApproxComp/sec-data.tex

The framework for speeding-up shortest path and distance queries with proxies consists of two modules: preprocessing and query answering

@@

@@

\stitle{(2) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}

The problem of {\em link prediction} or {\em link inference} is that of predicting the formation of future links in a dynamic and
evolving network. The link prediction problem has numerous
applications, such as the recommendation of friends in a social
network, the recommendation of images in a multimedia network, or
the recommendation of collaborators in a scientific network, therefore, link
prediction methods have been extensively studied  because of their numerous applications in various network-centered domains.

Link prediction methods are often applied to very large networks, which are also sparse.  The massive sizes of such networks can
create challenges for the prediction process in spite of their sparsity. This is because the {\em search space} for the link
prediction problem is of the size $O(n^2)$, where $n$ is the number of nodes. Quadratic scalability can rapidly become untenable for
larger networks. In fact, an often overlooked fact is that most {\em current link prediction algorithms evaluate the link
propensities only over a subset of possibilities rather than exhaustively search for link propensities over the entire network}, \eg \cite{dwang,lee,zhao2016,zhu2016}.

In order to understand why this is the case,
consider a network with $10^6$ nodes. Note that a size such as
$10^6$ is not large at all by modern standards, and even common
bibliographic networks such as DBLP now exceed this size. Even
for this modest network, the number of {\em possibilities} for links
is of the order of $10^{12}$. Therefore, a 1GHz processor would
require at least $10^3$ seconds just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much larger than $10^3$ seconds.  It is
instructive, therefore, to examine how this (lower bound on) running
time scales with increasing network size. Table~\ref{time} shows the
time requirements for allocating a single machine cycle to each
pair-wise possibility. The running time in this table represent
very optimistic lower bounds on the required time because link
prediction algorithms are complex and require far more than a single
machine cycle for processing a node-pair. Note that for larger
networks, even the presented lower bounds on the running time are
impractical.
\begin{table}
\caption{The $O(n^2)$ problem in link prediction: Time required to
allocate a {\em single machine cycle} to every node-pair possibility
in networks of varying sizes and processors of various speeds.}
\label{time}
\vspace{0ex}
\centering
\begin{tabular}{cccc}
\hline \hline Network Sizes & 1 GHz &  3 GHz & 10 GHz \\
\hline \hline $10^6$ nodes & 1000 sec. & 333 sec. & 100 sec.\\
\hline $10^7$ nodes & 27.8 hrs &  9.3 hrs &  2.78 hrs\\
\hline $10^8$ nodes & $>100$ days &  $>35$ days & $> 10$ days\\
\hline $10^9$ nodes & $>10000$ days & $>3500$ days & $> 1000$ days\\
\hline \hline
\end{tabular}
\vspace{-2ex}
\end{table}

It is noteworthy that most link prediction algorithms in the
literature are not designed to search over the entire space of
$O(n^2)$ possibilities. A closer examination of the relevant
publications shows that even for networks of modest size, these
algorithms perform benchmarking  only by evaluating over a {\em
sample of the possibilities} for links. This is only to be expected
in light of the lower bounds shown in Table~\ref{time}.  In other
words, the {\em complete ranking problem} for link prediction in
very large networks remains largely unsolved at least from a
computational point of view. It is evident from the presented lower
bounds in Table~\ref{time} that any ranking-based link prediction
algorithm {\em must integrate search space pruning} within the
prediction algorithm in order to even  have any  hope of exploring
the $O(n^2)$ search space in a reasonable amount of time. The
algorithmic design of most link prediction algorithms largely
overlooks this basic requirement~\cite{chancc,propflow}.

>>>>

The framework for speeding-up shortest path and distance queries with proxies consists of modules preprocessing and query answering as follows.

@@

without losing any accuracy

@@

\stitle{(2) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}. Link prediction is the task to predict the formation of future links in a dynamic and evolving network, and has been extensively studied due to its numerous applications, such as the recommendation of friends in a social network, images in a multimedia network, or
collaborators in a scientific network.

Link prediction methods are often applied to very large and sparse networks, which has a large {\em search space} $O(n^2)$, 
where $n$ is the number of nodes. Hence, the scalability is a big challenge. In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}, \eg \cite{zhu2016}.
In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
is of the order of $10^{16}$. Therefore, a 3GHz processor would
require at least $35$ days just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much much larger than $35$ days.

It is noteworthy that most existing link prediction algorithms are not designed to search over the entire 
$O(n^2)$ possibilities. A closer examination of the relevant
studies shows that even for networks of modest size, these
algorithms perform benchmark evaluations over a {\em
sample of the possibilities} for links.  In other
words, the {\em complete ranking problem for link prediction in
very large networks remains challenging at least from a
computational point of view}.

\eat{%%%%%%%
\begin{table}
\caption{The $O(n^2)$ problem in link prediction: Time required to
allocate a {\em single machine cycle} to every node-pair possibility
in networks of varying sizes and processors of various speeds.}
\label{time}
\vspace{0ex}
\centering
\begin{tabular}{cccc}
\hline \hline Network Sizes & 1 GHz &  3 GHz & 10 GHz \\
\hline \hline $10^6$ nodes & 1000 sec. & 333 sec. & 100 sec.\\
\hline $10^7$ nodes & 27.8 hrs &  9.3 hrs &  2.78 hrs\\
\hline $10^8$ nodes & $>100$ days &  $>35$ days & $> 10$ days\\
\hline $10^9$ nodes & $>10000$ days & $>3500$ days & $> 1000$ days\\
\hline \hline
\end{tabular}
\vspace{-2ex}
\end{table}
}%%%%%%%%%%%
